Practical Optional Types for Clojure

### 2015-07-08 formal-model.tex
Add feeds2imap experiment

For example, the `then' proposition for the expression $o$ is $\notprop{\falsy{}}{o}$.
This says if the expression $o$ evaluates to a true value, then $o$ is neither
of type \False or \Nil. Naturally, the `else' proposition $\isprop{\falsy{}}{o}$---which
is true when $o$ is a false value---
says $o$ is either \False or \Nil.

The pair of propositions are called a \emph{proposition set}, written {\filterset{\thenprop{\prop{}}}{\elseprop{\prop{}}}}.

@@

We extend the syntax in \figref{main:figure:javatyping} with Java field lookups and calls to
methods and constructors. 
To prevent ambiguity between zero-argument methods and fields, field accesses are written \fieldexp{\fld{}}{\e{}},
and method calls are written $\methodexp{\mth{}}{\e{}}{\overrightarrow{es}}$.
%and \clj{(new class es*)} is $\newexp{\class{}}{\overrightarrow{es}}$.

\egref{example:getparent-direct-constructor}, copied here,
$$
\clj{(.getParent (new File "a/b"))}
$$
is written
\begin{equation}  \label{eq:unresolved}
  \qquad {\methodexp {\getparent{}} {\newexp {\File{}} {\makestr{a/b}}} {}}
\end{equation}

>>>>

The `then' proposition {\thenprop{\prop{}}} for the variable $o$ is $\notprop{\falsy{}}{o}$, for example.
This says if the expression $o$ evaluates to a true value, then $o$ is neither
of type \False or \Nil. Naturally, the `else' proposition {\elseprop{\prop{}}} is $\isprop{\falsy{}}{o}$---which
is true when $o$ is a false value---says $o$ is either \False or \Nil.

The pair of propositions {\filterset{\thenprop{\prop{}}}{\elseprop{\prop{}}}} is called a \emph{proposition set}.

@@

We extend the syntax in \figref{main:figure:javatyping} with Java field lookups and calls to
methods and constructors. 
To prevent ambiguity, % between zero-argument methods and fields, 
field accesses are written \fieldexp{\fld{}}{\e{}}
and method calls $\methodexp{\mth{}}{\e{}}{\overrightarrow{e}}$.
%and \clj{(new class es*)} is $\newexp{\class{}}{\overrightarrow{es}}$.

\egref{example:getparent-direct-constructor} translates like so.
$$
\clj{(.getParent (new File "a/b"))}
$$
\begin{equation}  \label{eq:unresolved}
  \qquad {\methodexp {\getparent{}} {\newexp {\File{}} {\makestr{a/b}}} {}}
\end{equation}
